Wikipedia Text Mining and Entropy Analysis

### 2019-01-23 wiki_entropy/wiki_clustering.Rmd
nearly there with cosine comparison

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(missMDA)
library(cluster)
library(widyr)

@@

wf_sub <- wf_df %>%
  filter(feature %in% wf_many_langs$feature,
         language %in% wf_sub_langs$language) %>%
  dplyr::select(language, feature, value) %>%
  group_by(feature) %>%
  mutate(value = as.numeric(as.factor(value))) %>%
  group_by(feature) %>% # for each pair of language, does this feature assin them the same value
  nest() %>% #maps features to a table mapping languages to numerical factor feature values
  mutate(cors = map(data, my_pairwise_cor))
  select(-data) %>%
  unnest()

wf_comp <- wf_sub %$%
  data %>%
  do.call(cbind, args=.) 
wf_comp <- wf_comp[, -seq(3, length(wf_comp), 2)] #get values and one column of language

langs_to_compare <- wf_comp$language
wkpd_comp <- wkpd %>%
    filter(Language %in% langs_to_compare)

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(missMDA)
library(cluster)
library(widyr)
library(lsa)
library(magrittr)

@@

wf_sub <- wf_df %>%
  filter(feature %in% wf_many_langs$feature,
         language %in% wf_sub_langs$language) %>%
  dplyr::select(language, feature, value) %>%
  group_by(feature) %>%
  mutate(value = as.numeric(as.factor(value))) %>%
  group_by(feature) %>% # for each pair of language, does this feature assin them the same value
  nest() #maps features to a table mapping languages to numerical factor feature values
  # mutate(cors = map(data, my_pairwise_cor))
  # select(-data) %>%
  # unnest()

wf_comp <- wf_sub %$%
  data %>%
  do.call(cbind, args=.)

wf_comp <- wf_comp[, -seq(3, length(wf_comp), 2)] 
langs_to_compare <- wf_comp$language
wf_comp %<>% 
  as.data.frame(row.names=wf_comp$language)

wkpd_comp <- wkpd %>%
    filter(Language %in% langs_to_compare) 
wkpd_comp %<>% as.data.frame(row.names=wkpd_comp$Language)

lang_pairs <- langs_to_compare %>%
  combn(2, simplify = FALSE)

K <- length(lang_pairs)

lang_x <- lang_pairs %>%
    unlist() %>%
    matrix(nrow = K, byrow=TRUE) %>%
    as.data.frame() %>%
    mutate(wiki = lsa::cosine(wkpd_comp[V1, ], wkpd_comp[V2, ]), 
           wals = lsa::cosine(wf_comp[V1, ], wf_comp[V2, ]))
